### 2018-07-31 README.Rmd

# Benchmarking single-cell trajectory inference methods

Scripts to reproduce the manuscript

@@

```{r, echo = FALSE, message=FALSE}
datasets <- list_datasets() %>% group_by(dataset_source) %>% sample_n(1) %>% pull(dataset_id) %>% load_datasets()

>>>>

# Benchmarking trajectory inference methods

This repo contains the scripts to reproduce the manuscript

@@

```{r, echo = FALSE, message=FALSE}
set.seed(1)

datasets <- list_datasets() %>% group_by(dataset_source) %>% sample_n(1) %>% pull(dataset_id) %>% load_datasets()
